### 2021-07-28 doc/thesis/chapters/hls.tex
add audio output graphic

The program code example \ref{prog:axi4_lite} shows the specification of an AXI4-Lite memory-mapped slave interface.
The provided registers are separated into configuration registers and status registers.
The configuration is readable and writeable, while the status registers are implemented as read-only, which requires less logic in the RTL implementation.\\

@@

The second program code example \ref{prog:axi4_stream} demonstrates the equally simple definition of an AXI4-Stream interface.

>>>>

The code example in Program \ref{prog:axi4_lite} shows the specification of an AXI4-Lite memory-mapped slave interface.
The provided registers are separated into configuration registers and status registers.
The configuration is readable and writeable, while the status registers are implemented as read-only, which requires less logic in the RTL implementation.\\

@@

The second code example, Program \ref{prog:axi4_stream}, demonstrates the equally simple definition of an AXI4-Stream interface.
